Dirac neutrino mass generation from Majorana messenger

### 2019-08-12 draft.tex
lc

\subsection{Fermionic dark matter}
The relic density of DM is controlled by annihilation $\psi_{1} \psi_{1} \to l _{\alpha}^+ \overline{l}_{\beta}^- $, via Yukawa coupling $h^{a}_{i}$. These Yukawa couplings are restricted by CLFV and neutrino masses. %But, Yukawa couplings $y^{a}_{j}$ is free.

Because the particle $\psi_{1}$ only interacts with the leptons via the Yukawa couplings, this model has no a direct detection cross section at three level. In the case where the mass of the other fermions and scalars is nearly degenerated to $\psi_{1} $, the processes of coannihilation  can be relevant for the relic density calculation~\cite{Klasen:2013jpa}.

>>>>

\subsection{Fermionic dark matter}
The relic density of DM is controlled by the $Z'$ portal~\footnote{For
  a recent review of Majorana Dark matter with a $Z'$ portal
  see~\cite{Blanco:2019hah} } and
% check Ibarra papers
also through the annihilation
$\psi_{1} \psi_{1} \to l _{\alpha}^+ \overline{l}_{\beta}^- $, via
Yukawa coupling $h^{a}_{i}$. These Yukawa couplings are restricted by
CLFV and neutrino masses. %But, Yukawa couplings $y^{a}_{j}$ is free.
In the case where the mass of the other fermions and scalars is nearly
degenerated to $\psi_{1} $, the processes of coannihilation can be
relevant for the relic density calculation~\cite{Klasen:2013jpa}.

Because the particle $\psi_{1}$ only interacts with the leptons via the Yukawa couplings, this model has no a direct detection cross section at three level.
